
%------------------------------------------------
% Industry Bodies
%------------------------------------------------

\section{Industry Bodies}
\hrule

\medskip
\textbf{ATSC (Advanced Television Systems Committee)}
Not-for-profit developing voluntary standards for digital television.

\smallskip
\textbf{Cablelabs (Cable Television Laboratories)}
Not-for-profit innovation and R\&D lab. System operators from around the world are eligible to be members.

\smallskip
\textbf{DASH-IF (DASH Industry Forum}
Creates interoperability guidelines and promotes MPEG-DASH. Microsoft, Netflix, Google, Ericsson, Samsung and Adobe.

\smallskip
\textbf{DECE (Digital Entertainment Content Ecosystem)}
Inventor of \textit{Ultraviolet}, now dissolved.

\smallskip
\textbf{IETF (Internet Engineering Task Force)}
Responsible for the technical standards that comprise the Internet protocol suite (TCP/IP).

\smallskip
\textbf{ITU (International Telecommunication Union)}
UN agency that coordinates shared global use of the radio spectrum, satellite orbits and establishes worldwide standards.

\smallskip
\textbf{MPEG (Motion Picture Experts Group)}
Standards committee that sets policy for media encoding and decoding standards.

\smallskip
\textbf{MovieLabs}
Non-profit to R\&D Movie distribution and protection. (Disney, Paramount, Twentieth Century Fox, Sony Pictures, Universal, and Warner Bros).

\smallskip
\textbf{SMPTE (Society of Motion Picture \& Television Engineers)}
Global professional association of engineers, technologists, and execs working in the m\&E industy.

\smallskip
\textbf{W3C (World Wide Web Consortium)}
The main international standards organisation for the World Wide Web.
