%------------------------------------------------
% Monetisation
%------------------------------------------------

\section{Monetisation}
\hrule
\medskip
\textbf{AVOD (Advertising VOD)}
Advertising-based video on demand.

\smallskip
\textbf{Interstitial}
Any web-based advertisement which occurs before, after, or during a narrative content presentation. For example, if streaming media terminology were applied to regular television, standard television commercials would be called interstitials, since they interrupt programming.

\smallskip
\textbf{Post-roll}
Displaying a video advertisement after the primary video is played.

\smallskip
\textbf{Pre-roll}
Displaying a video advertisement occurring before the primary video is played. Pre-roll advertisements for online video are positioned similar to the way that movie trailers are shown prior to watching a movie at your local cineplex.

\smallskip
\textbf{PVOD (Premium VOD)}
Variation of TVOD where end-users can pay to access content sooner than others.

\smallskip
\textbf{PPV (Pay-Per-View)}

\smallskip
\textbf{SVOD (Subscription VOD)}
subscription video-on-demand. Similar to traditional cable television, SVOD grants customers access to a catalog of video content for a recurring daily, weekly, or monthly rate

\smallskip
\textbf{TVOD (Transactional VOD)}
transactional video on demand. Buying or renting a piece of content. In the case of live events, TVOD can also be known as Pay-Per-View (PPV).

\smallskip
\textbf{VAST (Video Ad Serving Template)}
XML schema for serving ads to digital video players, and describes expected video player behavior when executing VAST-formatted ad responses.
