\section{E-H}
\hrule

\medskip
\textbf{EME (Encrypted Media Extensions)}
API that enables web applications to interact with content protection systems. Enables encrypted files to be used in any browser regardless of the underlying protection system. Only capable of decrypting media data provided via \textit{MSE}.

\smallskip
\textbf{Encode}
Process of compressing RAW video, or the process of re-encoding a video into a different format.

\smallskip
\textbf{F4V (Flash H.264 Video)}
Adobe proprietary extension to H.264 \textit{Container}.

\smallskip
\textbf{FairPlay}
Apple \textit{DRM}, the only option for Safari and is only used by Apple devices.

\smallskip
\textbf{FFMPEG}
Open-source suite of libraries and programs for handling video \& audio.

\smallskip
\textbf{Fingerprint (Perceptual Hash)}
A generated hash of a video that will uniqely identify the video. Not to be confused with \textit{Watermark}.

\smallskip
\textbf{fMP4 (Fragmented MP4)}
Single \textit{MP4} file which contains a series of internal segments which can be requested individually from a HTTP server that supports byte-range requests.

\smallskip
\textbf{FPS (Frames Per Second)}
See \textit{Frame Rate}.

\smallskip
\textbf{Fragmentation}
Divide large media files into a series of smaller files with the purpose of delivering them over the internet.

\smallskip
\textbf{Frame Rate}
The number of frames per second (FPS). Common frame rates include 24 fps (film), 30 fps, and 29.97 fps.

\smallskip
\textbf{GOP (Group of Pictures)}
Logical grouping of \textit{frames} for compression pruposes. Each GOP begins with an I-frame keyframe and can contain any number of predictive (P frames) and bidirectional predictive (B frames).

\smallskip
\textbf{H.26[1|2|3|4|5|6]}
Standards-based Codecs:\\
 - \textit{H.262} also known as \textit{MPEG-2}.\\
 - \textit{H.264} also known as \textit{AVC} or  \textit{MPEG-4 Part 10}.\\
 - \textit{H.265} also known as \textit{HEVC} or \textit{MPEG-H}. 25\% to 50\% better compression at the same level of video quality, or substantially improved video quality at the same bit rate. It supports resolutions up to 8192×4320, including 8K \textit{UHD}.\\
 - \textit{H.266} also known as \textit{VVC}.

\smallskip
\textbf{HbbTV (Hybrid Broadcast Broadband TV)}
Standard for delivering content to consumers over broadcast and broadband networks.

\smallskip
\textbf{HDS (HTTP Dynamic Streaming)}
Adobe's \textit{ABR} method for on-demand and live - \textit{MP4} video content over HTTP.

\smallskip
\textbf{HDTV (High Definition Television)}
Broadcast and viewing of high-definition signals (720p progressive or 1080i).

\smallskip
\textbf{HEVC (High Efficiency Video Coding)}
See \textit{H.265}.

\smallskip
\textbf{HLS (HTTP Live Streaming)}
Protocol for delivering live streams by HTTP.  \textit{H.264} has to be used as the video \textit{codec}.
