\section{U-Z}
\hrule

\medskip
\textbf{Ultra HD}
Brand name for consumer 4K monitors.

\smallskip
\textbf{UltraViolet}
Defunct cloud-based digital rights locker.

\smallskip
\textbf{Unicast}
Streaming from one server, endpoint, or user. e.g. \textit{OTT}.  See also \textit{Multicast}.

\smallskip
\textbf{VAST (Video Ad Serving Template)}
XML schema for serving ads to digital video players, and describes expected video player behaviour when executing VAST-formatted ad responses.

\smallskip
\textbf{VBR (Variable Bitrate)}
Allows a higher bitrate (and therefore more storage space) to be allocated to the more complex segments of media files while less space is allocated to less complex segments.

\smallskip
\textbf{VITC (Vertical Interval Timecode)}
\textit{SMPTE} \textit{Timecode} encoded on one scan line in a video signal.

\smallskip
\textbf{VLC (VideoLan Client)}
A player capable of playing a wide variety of formats.

\smallskip
\textbf{vMVPD (Virtual Multichannel Video Programming Distributor)}
Provides multiple TV channels through the internet e.g. DirecTV Now, PlayStation Vue, YouTube TV. See also \textit{MVPD}.

\smallskip
\textbf{VOD (Video on demand)}
Interactive TV system that allows the viewer to select content and view it at a time of their choosing.

\smallskip
\textbf{Vorbis}
Open-source audio \textit{codec}.

\smallskip
\textbf{VP9}
Open and royalty-free video \textit{codec} developed by Google.

\smallskip
\textbf{VTM (VVC Test Model)}
Reference software codebase for testing \textit{VVC}.

\smallskip
\textbf{VTT (Video Text Track)}
Text file in the Web Video Text Tracks (WebVTT) format. Can include subtitles, captions, descriptions, chapters, and metadata.

\smallskip
\textbf{VVC (Versatile Video Coding)}
See \textit{H.266}.

\smallskip
\textbf{Watermark}
Embedding data into a video stream or overlaying onto the video for the purpose of later identifying where that video originate. Not to be confused with \textit{Fingerprint}.

\smallskip
\textbf{WebGL}
Designed for rendering 2D and 3D graphics, running in the browser with JavaScript. See also \textit{OpenGL}.

\smallskip
\textbf{WebM}
Codec created as VP8, purchased by Google and open-sourced.

\smallskip
\textbf{WebRTC (Web Real-Time Communication)}
Allows direct peer-to-peer real-time communication via APIs from browser with no plugins.

\smallskip
\textbf{Widevine}
Google \textit{DRM} - Used on Android Devices natively, in Chrome, Edge (soon), Roku, Smart TVs.

\smallskip
\textbf{Windows Media}
Microsoft's proprietary legacy media format that housed audio, video, and metadata.

\smallskip
\textbf{WMV (Windows Media Video)}
Series of video codecs and their corresponding video coding formats developed by Microsoft.

\smallskip
\textbf{YUV}
Full-colour video signal format, consisting of three elements: Y (luminance), and U and V (chrominance). See also \textit{RGB}.
