%------------------------------------------------
% Terms
%------------------------------------------------

%------------------------------------------------
\section{A}
\hrule

\medskip
\textbf{AAC (Advanced Audio Coding)}
Audio codec for online video and live streaming.

\smallskip
\textbf{ABR (Adaptive Bitrate Streaming)}
Choosing an appropriate \textit{Encode} quality dynamically by analysing the bandwidth and CPU.

\smallskip
\textbf{ADI (Asset Distribution Interface Specification)}
Means by which content as well as metadata are transported from a provider to an Asset Management System.

\smallskip
\textbf{AIFF (Audio Interchange File Format)}
Audio format developed by Apple.

\smallskip
\textbf{ASF (Advanced System Format)}
A \textit{Container} format defined by Microsoft for media files.

\smallskip
\textbf{ATSC (Advanced Television Systems Committee)}
Not-for-profit, developing voluntary standards for digital television.

\smallskip
\textbf{AVI (Audio Video Interleave)}
Proprietary \textit{Container} format by Microsoft, can contain both audio and video data in a file container.

\smallskip
\textbf{AVC (Advanced Video Coding)}
See \textit{H.264}.

\smallskip
\textbf{AVOD (Advertising VOD)}
Monetisation Model: Advertising supporting \textit{VOD}.


%------------------------------------------------
\section{B-C}
\hrule

\medskip
\textbf{Cablelabs (Cable Television Laboratories)}
Not-for-profit innovation and R\&D lab. System operators from around the world are eligible to be members.

\smallskip
\textbf{CBR (Constant Bitrate)}
Encoding each frame or \textit{GOP} at a constant bitrate.

\smallskip
\textbf{CDN}
Content Delivery Network.

\smallskip
\textbf{CENC (Common Encryption Scheme)}
Defines encryption-related metadata in a standard format for any \textit{DRM}.  Videos can be encrypted once and any decryption module can decrypt it.  Used with \textit{ISO BMFF}.

\smallskip
\textbf{Chrominance}
The color of a video signal. See also \textit{Y (Luminance)}.

\smallskip
\textbf{Chunking}
See \textit{Fragmentation}.

\smallskip
\textbf{Codec}
Compress \& Decompress (Encode \& Decode) standard for reducing the file sizes of video \& audio. Most common is \textit{H.264}.

\smallskip
\textbf{Container}
Wraps into a single file the encoded audio \& video and the metadata.  Popular containers are \textit{MP4} and \textit{AVI}.

%------------------------------------------------
\section{D}
\hrule

\medskip
\textbf{DASH-IF (DASH Industry Forum)}
Industry group creating interoperability guidelines and promoting \textit{MPEG-DASH}.

\smallskip
\textbf{dash.js}
Reference client implementation by \textit{DASH-IF} for the playback of \textit{MPEG-DASH} via JavaScript and compliant \textit{MSE} / \textit{EME} platforms.

\smallskip
\textbf{DAM (Digital Asset Managment)}
See \textit{MAM}.

\smallskip
\textbf{DASH (Dynamic Adaptive Streaming via HTTP)}
\textit{ABR} that enables streaming of content over the Internet delivered HTTP server. DASH does not require a specific \textit{codec} - the video could be encoded using \textit{H.264}, \textit{VP9}, \textit{H.265}, etc.

\smallskip
\textbf{DECE (Digital Entertainment Content Ecosystem)}
Inventor of \textit{Ultraviolet}, now dissolved.

\smallskip
\textbf{DRM (Digital Rights Management)}
Access control technologies that limit the usage \& sharing of digital content.

\smallskip
\textbf{DOCSIS (Data Over Cable Service Interface Specification)}
Telco standard that permits the addition of high-bandwidth data transfer to an existing cable television (CATV) system.

\smallskip
\textbf{Deinterlace}
To process interlaced TV video. Uses every other line from one field \& interpolates new in-between lines. See also \textit{Interlace}.

\smallskip
\textbf{DVB (Digital Video Broadcasting)}
Open standards for digital TV.  Satalite [DVB-S, DVB-S2], Cable [DVB-SH, DVB-C, DVB-C2], Terrestrial TV [DVB-T, DVB-T2].

%------------------------------------------------
\section{E-F}
\hrule

\medskip
\textbf{Encode}
Process of compressing RAW video, or the process of re-encoding a video into a different format.

\smallskip
\textbf{EME (Encrypted Media Extensions)}
API that enables web applications to interact with content protection systems. Enables encrypted files to be used in any browser regardless of the underlying protection system.

\smallskip
\textbf{FairPlay}
Apple DRM - Cipher Block Chaining encryption, the only option for Safari and is only used by Apple devices.

\smallskip
\textbf{Fragmentation}
Process of dividing a larger file into a series of smaller files with the purpose of delivering them over the internet.

\textbf{Frame Rate}
The number of frames per second (FPS) for cinema or video acquisition, editing and projection. Common frame rates include 24 fps (film), 30 fps, and 29.97 fps.

\textbf{FPS (Frames Per Second)}
See \textit{Frame Rate}.

\smallskip
\textbf{Fingerprint (Perceptual Hash)}
A generated hash of a video that will uniqely identify the video. See also \textit{Watermark}.

\smallskip
\textbf{fMP4 (Fragmented MP4)}
\textit{MP4} which contains a series of segments which can be requested individually from a HTTP server that supports byte-range requests.

\smallskip
\textbf{F4V (Flash H.264 Video)}
Flash MP4 Video.  Adobe proprietary extension to designate MPEG-4 H.264 content in a Flash-compliant \textit{Container}.

%------------------------------------------------
\section{G-H}
\hrule

\medskip
\textbf{HDTV (High Definition Television)}
Broadcast and viewing of high-definition signals (720p progressive or 1080i).

\smallskip
\textbf{H.26[1|2|3|4|5|6]}
Standards-based Codecs:\\
 - \textit{H.262} also known as \textit{MPEG-2}.\\
 - \textit{H.264} also known as \textit{AVC} or  \textit{MPEG-4 Part 10}.\\
 - \textit{H.265} also known as \textit{HEVC} or \textit{MPEG-H}. 25\% to 50\% better compression at the same level of video quality, or substantially improved video quality at the same bit rate. It supports resolutions up to 8192×4320, including 8K \textit{UHD}.\\
 - \textit{H.266} also known as \textit{VVC}.

\smallskip
\textbf{HDS (HTTP Dynamic Streaming)}
Adobe's \textit{ABR} method for on-demand and live - \textit{MP4} video content over HTTP.

\smallskip
\textbf{HEVC (High Efficiency Video Coding)}
See \textit{H.265}.

\smallskip
\textbf{HbbTV (Hybrid Broadcast Broadband TV)}
Standard for delivering content to consumers for consumption on TV displays over broadcast and broadband networks.

\smallskip
\textbf{HLS (HTTP Live Streaming)}
Protocol for delivering live streams by HTTP.  \textit{H.264} has to be used as the video \textit{codec}.

\smallskip
\textbf{GOP (Group of Pictures)}
Grouping of \textit{frames} for compression. Longer GOPs allow better compression but slow the delivery process for live encoding. Each GOP begins with an I-frame keyframe and can contain any number of predictive (P frames) and bidirectional predictive (B frames).


%------------------------------------------------
\section{I-K}
\hrule

\medskip
\textbf{Interlace}
Technique for doubling the perceived frame rate of a video display without consuming extra bandwidth. See also \textit{Deinterlace}.

\smallskip
\textbf{ISO BMFF (ISO Base Media File Format)}
\textit{Container} file format.  Basis for other media file formats (e.g. the \textit{MP4} \textit{Container}).

\smallskip
\textbf{I Frame (Intra picture frame)}
See \textit{GOP}.

\smallskip
\textbf{Keyframe}
Stores the complete image of the scene.

\smallskip
\textbf{IETF (Internet Engineering Task Force)}
Responsible for the technical standards that comprise the Internet protocol suite (TCP/IP).

\smallskip
\textbf{ITU (International Telecommunication Union)}
UN agency that coordinates shared global use of the radio spectrum, satellite orbits and establishes worldwide standards.

\smallskip
\textbf{IPTV (Internet Protocol television)}
TV content over IP as opposed to terrestrial, satellite, or cable.

\smallskip
\textbf{Interstitial}
Any web-based advertisement which occurs before, after, or during a narrative content presentation.

%------------------------------------------------
\section{L-M}
\hrule

\smallskip
\textbf{Luminance (Y)}
The intensity or brightness of a video signal. See also \textit{Chrominance}.

\smallskip
\textbf{LITC (Linear Timecode)}
\textit{SMPTE} \textit{Timecode} data in an audio signal.

\smallskip
\textbf{LCEVC (Low Complexity Enhancement Video Coding)}
Takes a base video codec such as \textit{AVC} and employs an efficient low-complexity enhancement that correct artifacts produced by the base video codec and adds detail and sharpness for the final output video.

\smallskip
\textbf{MSE (Media Source Extensions)}
Media Source Extensions.

\smallskip
\textbf{m3u8}
Playlist file.  Can be used to define a playlist for delivery to smart TV devices such as Roku.

\smallskip
\textbf{MBR (Multi-bitrate Streaming}
Sending out multiple versions of the same live stream at different quality levels.

\smallskip
\textbf{MP4}
\textit{Container} format.

\smallskip
\textbf{MPEG-DASH}
See \textit{DASH}.

\smallskip
\textbf{MPEG-[1|2|3|4|H]}
See \textit{H.26[1|2|3|4|5]}.

\smallskip
\textbf{Multicast}
Streaming from one server to many end points simultaneously e.g. \textit{IPTV}.  See also \textit{Unicast}.

\smallskip
\textbf{MPEG (Motion Picture Experts Group)}
Standards committee that sets policy for media encoding and decoding standards.

\smallskip
\textbf{MAM (Media Asset Management)}
Repository for large media files, such as video and full-resolution images. Often called \textit{DAM}'s.

\smallskip
\textbf{Marlin}
Open-standard DRM. Most widely used DRMs in Japan, China, and parts of East Asia.

\smallskip
\textbf{MP4}
Container Format.

\smallskip
\textbf{Multiplex}
A term describing the interleaving of multple signals together into a single signal. Multiplexing is often shortened even further to the term "muxing" and a pertient example of muxing is the conversion of MPEG-2 program or elementary streams into an MPEG-2 transport stream for broadcast delivery

\smallskip
\textbf{Muxing}
See \textit{Multiplex}.

\smallskip
\textbf{MovieLabs}
Non-profit to R\&D Movie distribution and protection. (Disney, Paramount, Twentieth Century Fox, Sony Pictures, Universal, and Warner Bros).

\smallskip
\textbf{Movielabs Digital Distribution Framework}
Family of complementary, compatible specifications that address key aspects of online delivery e.g. facilitating automation.

\smallskip
\textbf{MSO (Multiple System Operator)}
Companies that offer services beyond TV broadcast e.g. Internet and telephone alongside TV.  See \textit{MVPD}.

\smallskip
\textbf{MVPD (Multichannel Video Programming Distributor)}
Company that provides multiple TV channels e.g. Sky, BT, Comcast, DirecTV. Also known as \textit{MSOs}. See also \textit{vMVPD}.

\smallskip
\textbf{MVNO (Mobile Virtual Network Operator)}
Reseller of network services from other telecommunications suppliers and who does not own the telecommunication infrastructure.


%------------------------------------------------
\section{N-O}
\hrule

\medskip
\textbf{NDI (Network Device Interface)}
Specification to enable video-compatible products to communicate video in frame accurate and suitable for switching in a live production.

\smallskip
\textbf{Narrowcast}
To send data to a specific list of recipients.

\smallskip
\textbf{NTSC (National Television Standards Committee)}
A television video format used in the United States and elsewhere. Displayed 525 lines of resolution at 60 fields per second, 30 frames per second (actually a fractional value near 29.97). See also \textit{PAL}.

\smallskip
\textbf{Ogg}
An open-source container format that primarily houses \textit{Theora} and \textit{Vorbis}.

\smallskip
\textbf{OpenGL}
Cross-language and platform API to render 2D and 3D vector graphics normally used for desktop Apps, written in C.

\smallskip
\textbf{OBS (Open Broadcaster Software)}
Free and open source software for video recording and live streaming.

\smallskip
\textbf{OTT (Over The Top)}
Service offered directly to viewers via the Internet. OTT bypasses cable, broadcast, and satellite television platforms. e.g. Netflix.

\smallskip
\textbf{OVP (Online Video Platform)}
Platform that allows you to stream video content as well as upload your own produced content e.g. Dacast, JW Player, Kaltura.


%------------------------------------------------
\section{P}
\hrule

\medskip
\textbf{Pre-roll}
Displaying a video advertisement occurring before the primary video is played. Pre-roll advertisements for online video are positioned similar to the way that movie trailers are shown prior to watching a movie at your local cineplex.

\smallskip
\textbf{Progressive Download}
A method of delivering audio/video data over the Internet that involves playing a segment, often the initial downloaded portion of a file, while the remaining content download is still in progress.

\smallskip
\textbf{Progressive Video}
Video consisting of complete frames, not interlaced fields. Each individual frame is a coherent image captured by the camera at a single moment in time. See also interlaced video.

\smallskip
\textbf{PlayReady}
Microsoft DRM - Supported on Windows, most set-top boxes and TVs, uses WRMHEADER tag objects as metadata format

\smallskip
\textbf{Perceptual Compression}
A compression technique that takes advantage of knowledge of how humans perceive; that is, by eliminating visual detail that the eye cannot easily see or audio frequencies that the ear cannot easily hear.

\smallskip
\textbf{PAL (Phase Alternation Line)}
Television video format used in Europe and elsewhere. Displayed with 625 lines of resolution at 50 fields per second, 25 frames per second. See also \textit{NTSC}.

\smallskip
\textbf{Post-roll}
Displaying a video advertisement after the primary video is played.

\smallskip
\textbf{PVOD (Premium VOD)}
Variation of TVOD where end-users can pay to access content sooner than others.

\smallskip
\textbf{PPV (Pay-Per-View)}
Lorem.


%------------------------------------------------
\section{Q-R}
\hrule

\medskip
\textbf{RTSPE}
RTSPE

\smallskip
\textbf{RTSP}
RTSP

\smallskip
\textbf{RTMP (Real-Time Multimedia Protocol)}
Protocol for live streaming often use to deliver a stream from encoder to OVP endpoint for ingestion.

\smallskip
\textbf{RTP (Real-time Transport Protocol)}
Network protocol for delivering audio and video over IP networks.

\smallskip
\textbf{RGB}
Acronym for Red, Green, Blue. Full-color video signal format, consisting of three elements. See also YUV.

\smallskip
\textbf{Rights Holder}
Lorem.

%------------------------------------------------
\section{S}
\hrule

\medskip
\textbf{Segmenting}
See "Fragmentation".

\smallskip
\textbf{Simulcast (Simultaneous Broadcast)}
A broadcast that is coordinated between two or more mediums, such as radio and television.

\smallskip
\textbf{Smooth Streaming}
Microsoft’s proprietary adaptive-bitrate (ABR) technology, Smooth Streaming uses fragmented MP4 (ISO Base Media File Format) and the Protected Interoperable File Format (PIFF) to deliver small-file-segment streaming via HTTP. Smooth Streaming has been somewhat deprecated by Microsoft’s embrace of DASH as an industry standard.

\smallskip
\textbf{SVC (Scalable Video Coding)}
Lorem

\smallskip
\textbf{SMPTE (Society of Motion Picture \& Television Engineers)}
Global professional association of engineers, technologists, and execs working in the m\&E industy.

\smallskip
\textbf{SVOD (Subscription VOD)}
subscription video-on-demand. Similar to traditional cable television, SVOD grants customers access to a catalog of video content for a recurring daily, weekly, or monthly rate


%------------------------------------------------
\section{T}
\hrule

\medskip
\textbf{TS (Video Transport Stream)}
Video data compressed with standard MPEG-2. Often utilised for saving video on a DVD or broadcast video.


\smallskip
\textbf{TriCaster}
Enterprise encoders from made by NewTek.

\smallskip
\textbf{TeraDek}
TeraDek is a producer of high-quality hardware encoders.


\smallskip
\textbf{Theora}
Open-source video \textit{codec}..

\smallskip
\textbf{Transcode}
Process of creating copies of video files in different sizes.

\smallskip
\textbf{Timecode}
An exact time used to identify a specific frame in a clip or production. Measured in hours, minutes, seconds, and frames. Primary types are \textit{SMPTE}, \textit{LITC} and \textit{VITC}.

\smallskip
\textbf{Timecode}
A measurement of video frames, using an absolute reference point between each field or frame of video. Two primary types of

\smallskip
\textbf{TVOD (Transactional VOD)}
transactional video on demand. Buying or renting a piece of content. In the case of live events, TVOD can also be known as Pay-Per-View (PPV).


%------------------------------------------------
\section{U}
\hrule

\medskip
\textbf{UltraViolet}
Defunct cloud-based digital rights locker for films and television programs that allowed consumers to store proofs-of-purchase of licensed content in an account to enable playback on different devices using multiple applications from several different streaming services.

\smallskip
\textbf{Ultra HD}
The industry brand name for consumer 4K monitors is Ultra HD (UHD)

\smallskip
\textbf{Unicast}
Streaming from one server a single endpoint or user. e.g. \textit{OTT}.  See also \textit{Multicast}.


%------------------------------------------------
\section{V}
\hrule

\medskip
\textbf{VAST (Video Ad Serving Template)}
XML schema for serving ads to digital video players, and describes expected video player behavior when executing VAST-formatted ad responses.

\smallskip
\textbf{VP9}
VP9 is an open and royalty-free video coding format developed by Google, competes mainly with MPEG's High Efficiency Video Coding (HEVC/H.265).

\smallskip
\textbf{VBR (Variable Bitrate)}
VBR allows a higher bitrate (and therefore more storage space) to be allocated to the more complex segments of media files while less space is allocated to less complex segments.

\smallskip
\textbf{Vorbis}
Open-source audio \textit{codec}.

\smallskip
\textbf{VidBlasterX}
Software encoder for producing and streaming live events.

\smallskip
\textbf{vMix}
Software encoder for producing and streaming live events.

\smallskip
\textbf{VLC (VideoLan Client)}
A player capable of playing a wide variety of formats.

\smallskip
\textbf{VITC (Vertical Interval Timecode)}
\textit{SMPTE} \textit{Timecode} encoded on one scan line in a video signal.

\smallskip
\textbf{VBR}
Acronym for Variable Bit Rate. A compression scheme in which each unit of input material can be compressed to different sizes. For MPEG-2 video, for example, this means that "easier" sequences (that is, with no motion) can compress to very small sizes, whereas "hard" sequences (with lots of motion and scene cuts) can compress to much larger sizes. VBR compression can take better advantage of the overall available bandwidth of a video transmission or DVD player by allocating the available bits intelligently to the difficult parts of a sequence. See also CBR.

\smallskip
\textbf{VVC (Versatile Video Coding)}
See \textit{H.266}.

\smallskip
\textbf{VTM (VVC Test Model)}
Reference software codebase for testing \textit{VVC}.

\smallskip
\textbf{VOD (Video on demand)}
Interactive TV system that allows the viewer to select content and view it at a time of his or her own choosing.

\smallskip
\textbf{vMVPD (Virtual Multichannel Video Programming Distributor)}
Provides multiple TV channels through the internet e.g. DirecTV Now, PlayStation Vue, YouTube TV. See also \textit{MVPD}.

%------------------------------------------------
\section{W}
\hrule

\medskip
\textbf{WebRTC (Web Real-Time Communication)}
Allows direct peer-to-peer real-time communication via APIs from browser with no plugins.


\smallskip
\textbf{Windows Media}
Microsoft's proprietary legacy media format that housed audio, video, and metadata.

\smallskip
\textbf{WebM}
Codec created as VP8, purchased by Google and open-sourced.

\smallskip
\textbf{Widevine}
Google DRM - Used on Android Devices natively, in Chrome, Edge (soon), Roku, Smart TVs, uses protobuf format for metadata.

\smallskip
\textbf{Watermark}
Lorem. See also \textit{Fingerprint}.

\smallskip
\textbf{WebGL}
Designed for rendering 2D and 3D graphhics, running in the browser with Javascript. See also \textit{OpenGL}.

\smallskip
\textbf{WMV (Windows Media Video)}
Series of video codecs and their corresponding video coding formats developed by Microsoft.



%------------------------------------------------
\section{X-Z}
\hrule

\medskip
\textbf{YUV}
Full-color video signal format, consisting of three elements: Y (luminance), and U and V (chrominance). See also \textit{RGB}.
