\section{M-P}
\hrule

\medskip
\textbf{m3u8}
Playlist file.

\smallskip
\textbf{MAM (Media Asset Management)}
Repository for large media files, such as video and full-resolution images. Often called \textit{DAM}'s.

\smallskip
\textbf{Marlin}
Open-standard \textit{DRM}. Widely used in Japan, China, \& East Asia.

\smallskip
\textbf{MBR (Multi-bitrate Streaming)}
Sending out multiple versions of the same live stream at different quality levels.

\smallskip
\textbf{MovieLabs}
Non-profit to R\&D Movie distribution and protection. (Disney, Paramount, Twentieth Century Fox, Sony Pictures, Universal, and Warner Bros).

\smallskip
\textbf{MovieLabs Digital Distribution Framework}
Family of complementary, compatible specifications that address key aspects of online delivery e.g. facilitating automation.

\smallskip
\textbf{MP4}
\textit{Container} format.

\smallskip
\textbf{MPEG (Motion Picture Experts Group)}
Standards committee that sets policy for media encoding and decoding standards.

\smallskip
\textbf{MPEG-[1|2|3|4|H]}
See \textit{H.26[1|2|3|4|5]}.

\smallskip
\textbf{MPEG-DASH}
See \textit{DASH}.

\smallskip
\textbf{MSE (Media Source Extensions)}
Spec for JavaScript to send byte streams to media \textit{codecs} within Web browsers.

\smallskip
\textbf{MSO (Multiple System Operator)}
Companies that offer services beyond TV broadcast e.g. Internet and telephone alongside TV.  See \textit{MVPD}.

\smallskip
\textbf{Multicast}
Streaming from one server to many end points simultaneously e.g. \textit{IPTV}.  See also \textit{Unicast}.

\smallskip
\textbf{Multiplex}
Interleaving of multiple signals together into a single signal.

\smallskip
\textbf{Muxing}
See \textit{Multiplex}.

\smallskip
\textbf{MVNO (Mobile Virtual Network Operator)}
Reseller of network services from other telecommunications suppliers and who does not own the telecommunication infrastructure.

\smallskip
\textbf{MVPD (Multichannel Video Programming Distributor)}
Company that provides multiple TV channels e.g. Sky, BT, Comcast, DirecTV. Also known as \textit{MSOs}. See also \textit{vMVPD}.

\smallskip
\textbf{NAB (National Association of Broadcasters)}
Annual trade show held in April in Las Vegas.

\smallskip
\textbf{Narrowcast}
Send data to specific list of recipients.

\smallskip
\textbf{NDI (Network Device Interface)}
Specification to enable video-compatible products to communicate video in frame accurate and suitable for switching in a live production.

\smallskip
\textbf{Nielsen Ratings}
Audience measurement system that seeks to determine the audience size of TV programming in the US.

\smallskip
\textbf{NTSC (National TV Standards Committee)}
U.S. Video format. See also \textit{PAL}.

\smallskip
\textbf{OBS (Open Broadcaster Software)}
Open source video recording and live streaming.

\smallskip
\textbf{Ogg}
An open-source \textit{container} format that primarily houses \textit{Theora} and \textit{Vorbis}.

\smallskip
\textbf{OpenGL}
Cross-language and platform API to render 2D and 3D vector graphics.  Normally used for desktop Apps, written in C. See also \textit{WebGL}.

\smallskip
\textbf{OTT (Over The Top)}
Service offered directly to viewers via the Internet. OTT bypasses cable, broadcast, and satellite television platforms. e.g. Netflix.

\smallskip
\textbf{OVP (Online Video Platform)}
Platform that allows you to stream video content as well as upload your own produced content e.g. Dacast, JW Player.

\smallskip
\textbf{PAL (Phase Alternation Line)}
Television video format used in Europe and elsewhere. Displayed with 625 lines of resolution at 50 fields per second, 25 frames per second. See also \textit{NTSC}.

\smallskip
\textbf{Perceptual Compression}
Technique that eliminates visual detail that the eye cannot see or audio frequencies that the ear cannot hear.

\smallskip
\textbf{PlayReady}
Microsoft \textit{DRM} - Supported on Windows, most STBs and TVs.

\smallskip
\textbf{Post-roll}
Displaying a video advertisement after the primary video is played.

\smallskip
\textbf{Pre-roll}
Displaying a video advertisement before the primary video is played.

\smallskip
\textbf{Progressive Download}
A method of delivering audio/video data over the Internet that involves playing a segment, often the initial downloaded portion of a file, while the rest is downloading.

\smallskip
\textbf{Progressive Video}
Video consisting of complete frames, not interlaced fields. Each individual frame is a coherent image captured by the camera at a single moment in time. See also \textit{Interlaced}.

\smallskip
\textbf{PVOD (Premium VOD)}
Monetisation Model - Variation of \textit{TVOD} where end-users can pay to access content sooner than others.
