\section{I-L}
\hrule

\medskip
\textbf{I Frame (Intra picture frame)}
See \textit{GOP}.

\smallskip
\textbf{IBC (International Broadcasting Convention)}
Annual Conference \& Trade Show, held during September in Amsterdam.

\smallskip
\textbf{IETF (Internet Engineering Task Force)}
Responsible for the technical standards of TCP/IP.

\smallskip
\textbf{Interlace}
Technique for doubling the perceived frame rate of a video display without consuming extra bandwidth. See also \textit{Deinterlace}.

\smallskip
\textbf{Interstitial}
Any web-based advertisement which occurs before, after, or during the main content.

\smallskip
\textbf{IPTV (Internet Protocol television)}
TV content over IP as opposed to terrestrial, satellite, or cable.

\smallskip
\textbf{ISO BMFF (ISO Base Media File Format)}
\textit{Container} file format.  Basis for other media file formats (e.g. the \textit{MP4} \textit{Container}).

\smallskip
\textbf{ITU (International Telecommunication Union)}
UN agency that coordinates shared global use of the radio spectrum, satellite orbits and establishes worldwide standards.

\smallskip
\textbf{Keyframe}
A frame of video that contains all of the detail of the scene.

\smallskip
\textbf{LCEVC (Low Complexity Enhancement Video Coding)}
Takes a base video \textit{Codec} such as \textit{AVC} and employs an efficient low-complexity enhancement that correct artifacts produced by the base video codec and adds detail and sharpness for the final output video.

\smallskip
\textbf{LITC (Linear Timecode)}
\textit{SMPTE} \textit{Timecode} data in an audio signal.

\smallskip
\textbf{Luminance (Y)}
The intensity or brightness of a video signal. See also \textit{Chrominance}.
