\section{Q-T}
\hrule

\medskip
\textbf{RGB}
Acronym for Red, Green, Blue. Full colour video signal format, consisting of three elements. See also \textit{YUV}.

\smallskip
\textbf{RIST (Reliable Internet Stream Transport)}
Video transport protocol of live video content in real time at low latency over unmanaged networks.

\smallskip
\textbf{RTMP (Real-Time Messaging Protocol)}
Protocol for live streaming often use to deliver a stream from encoder to \textit{OVP} endpoint for ingestion.

\smallskip
\textbf{RTP (Real-Time Transport Protocol)}
Delivers audio and video over IP networks.

\smallskip
\textbf{RTSP (Real-Time Streaming Protocol)}
Establishes and controls media sessions between endpoints, allowing commands such as play, record and pause to control the media streaming from the server to a client.

\smallskip
\textbf{Segmenting}
See \textit{Fragmentation}.

\smallskip
\textbf{Simulcast (Simultaneous Broadcast)}
A broadcast that is coordinated between two or more mediums, such as radio and television.

\smallskip
\textbf{Smooth Streaming}
Microsoft’s proprietary \textit{ABR} technology. Uses \textit{fMP4} and \textit{PIFF} to stream via HTTP.

\smallskip
\textbf{SMPTE (Society of Motion Picture \& Television Engineers)}
Association of engineers, technologists, and execs working in the M\&E industry.

\smallskip
\textbf{SRT (Secure Reliable Transport) Protocol}
Open-source video transport protocol and technology stack. Alternative to \textit{RTMP} to transport low-latency streams over noisy networks.

\smallskip
\textbf{SSAI (Server-Side Ad Insertion)}
See \textit{DAI}.

\smallskip
\textbf{SVOD (Subscription VOD)}
Grants customers access to a catalogue of video content for a recurring daily, weekly, or monthly rate.

\smallskip
\textbf{Theora}
Open-source video \textit{Codec}.

\smallskip
\textbf{Timecode}
An exact time used to identify a specific frame in a clip or production. Measured in hours, minutes, seconds, and frames. Primary types are \textit{SMPTE}, \textit{LITC} and \textit{VITC}.

\smallskip
\textbf{Transcode}
Conversion of one type of \textit{encoded} data (video or audio) to another.

\smallskip
\textbf{Trick Play}
Visual feedback from the player while user is rewinding or fast-forwarding a stream.

\smallskip
\textbf{TS (Video Transport Stream)}
Video data compressed with standard MPEG-2. Often utilised for saving video on a DVD or broadcast video.

\smallskip
\textbf{TVOD (Transactional VOD)}
Monetisation Model - Buying or renting a piece of content.
